Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-17 paper.tex
better explanation of distance metric

\subsection{Generalizing to hand drawings}
A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We train the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}).~\remark{Process should be described (in supplement)}
Our neurally-guided SMC procedure
used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in section~\ref{neuralNetworkSection}).
But pixel-wise distance fares poorly on hand drawings, which never exactly match
the model's renders.
So, for hand drawings,
we \emph{learn} a surrogate likelihood function,
$L_{\text{learned}}(\cdot|\cdot)$.
The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
the distance between two traces conditioned upon their renderings.
We train our likelihood surrogate to approximate the symmetric difference:
\begin{equation}
-\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
  \end{equation}

We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
These were drawn reasonably carefully but not perfectly.
Because our model assumes that objects are snapped to a $16\times 16$ grid,
we made the drawings on graph paper.
\begin{figure}\centering
  \begin{minipage}{0.45\textwidth}
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}%
   \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
    \caption{(a): a hand drawing. (b): Rendering of the trace our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\ref{handDrawingExamples}
  \end{minipage}\hfill
  \begin{minipage}{0.45\textwidth}
  \includegraphics[width = 6cm]{figures/drawingAccuracy.png}
  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
    \end{minipage}
\end{figure}

\begin{figure}[H]
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-10.png}
    \includegraphics[width = 2cm]{figures/10-parse.png}    
    \subcaption{Noisy input}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-21.png}
    \includegraphics[width = 2cm]{figures/21-parse.png}    
    \subcaption{A graphical model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-77.png}
    \includegraphics[width = 2cm]{figures/77-parse.png}    
    \subcaption{A figure from a deep learning textbook}
    \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-0.png}
    \includegraphics[width = 2cm]{figures/0-parse.png}    
    \subcaption{Near miss}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-38.png}
    \includegraphics[width = 2cm]{figures/38-parse.png}    
    \subcaption{Failing on a Ising model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-34.png}
    \includegraphics[width = 2cm]{figures/34-parse.png}     
    \subcaption{Illusory contours}
    \end{minipage}
  \caption{Example drawings above model outputs. See also Fig.~\ref{firstPageExamples}}\label{handDrawingExamples}~\remark{Showing `failure cases' (the last three above) out-of-context seems not great. Perhaps remind people in the caption that stochastic search can help correct some of these issues?}
\end{figure}
For each drawing we annotated a ground truth trace, and evaluated the
model by asking it to sample many candidate traces for each drawing.
For 55\% of the drawings the Top-1 most likely sample exactly matches the
ground truth; as we consider more samples the model encounters traces
that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
Because our current model sometimes makes mistakes on hand drawings,
we envision the current system working as follows:
a user sketches a diagram,
and the system responds by proposing a few candidate interpretations.
The user could then select the one closest to their intention and edit it if necessary.

>>>>

\subsection{Generalizing to hand drawings}
A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We train the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}).~\remark{Process should be described (in supplement)}
Our neurally-guided SMC procedure
used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in section~\ref{neuralNetworkSection}).
But pixel-wise distance fares poorly on hand drawings, which never exactly match
the model's renders.
So, for hand drawings,
we \emph{learn} a surrogate likelihood function,
$L_{\text{learned}}(\cdot|\cdot)$.
The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
the distance between two traces conditioned upon their renderings.
We train our likelihood surrogate to approximate the symmetric difference,
which is  the number of drawing commands by which to traces differ:
\begin{equation}
-\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
\end{equation}
Intuitively, Eq.~\ref{symmetricDistance} says that
$L_{\text{learned}}(\cdot|\cdot)$ approximates the distance between
the trace we want and the trace we have so far.  Pixel-wise distance
metrics are sensitive to the fine details of how and exactly where
arrows, dashes, and corners are drawn -- but we wish to be invariant
to these details. So, we learn a distance metric over images that
approximates the distance metric in the search space over traces.

We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
These were drawn reasonably carefully but not perfectly.
Because our model assumes that objects are snapped to a $16\times 16$ grid,
we made the drawings on graph paper.
\begin{figure}\centering
  \begin{minipage}{0.45\textwidth}
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}%
   \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
    \caption{(a): a hand drawing. (b): Rendering of the trace our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\label{handDrawingExamples}
  \end{minipage}\hfill
  \begin{minipage}{0.45\textwidth}
  \includegraphics[width = 6cm]{figures/drawingAccuracy.png}
  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
    \end{minipage}
\end{figure}

\begin{figure}[H]
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-10.png}
    \includegraphics[width = 2cm]{figures/10-parse.png}    
    \subcaption{Noisy input}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-21.png}
    \includegraphics[width = 2cm]{figures/21-parse.png}    
    \subcaption{A graphical model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-77.png}
    \includegraphics[width = 2cm]{figures/77-parse.png}    
    \subcaption{A figure from a deep learning textbook}
    \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-0.png}
    \includegraphics[width = 2cm]{figures/0-parse.png}    
    \subcaption{Near miss}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-38.png}
    \includegraphics[width = 2cm]{figures/38-parse.png}    
    \subcaption{Failing on a Ising model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-34.png}
    \includegraphics[width = 2cm]{figures/34-parse.png}     
    \subcaption{Illusory contours}
    \end{minipage}
  \caption{Example drawings above model outputs. See also Fig.~\ref{firstPageExamples}}\label{lotsOfHandDrawings}~\remark{Showing `failure cases' (the last three above) out-of-context seems not great. Perhaps remind people in the caption that stochastic search can help correct some of these issues?}
\end{figure}
For each drawing we annotated a ground truth trace, and evaluated the
model by asking it to sample many candidate traces for each drawing.
For 55\% of the drawings the Top-1 most likely sample exactly matches the
ground truth; as we consider more samples the model encounters traces
that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
Because our current model sometimes makes mistakes on hand drawings,
we envision the current system working as follows:
a user sketches a diagram,
and the system responds by proposing a few candidate interpretations.
The user could then select the one closest to their intention and edit it if necessary.
